### 2024-02-01 paper.tex
rm last todos

\new{
These extensive benchmarks confirmed that our proposed combination of methods, i.e.\ using the shrunken means of residuals of VMRs for dimensionality reduction, is able to distinguish diverse cellular properties such as cell type, colorectal cancer stage (normal tissue, primary tumour, metastasis), embryonic stage, and germ layer (Fig.~\ref{fig:resource_usage}).
Our benchmarks also quantify how groups of cells become more readily separated in larger data sets.
As the neighbor score started to plateau at approximately 1000 cells, we propose that this represents a reasonable target cell number for future scBS studies. \todo{We may want to omit these last two sentences, as they might invite too much debate.}
}

@@

SA and LPMK acknowledge funding by the Klaus Tschira Foundation (project 00.022.2019).
LPMK, MMB, LK, SC, and AMV acknowledge funding from the European Commission via ERC grant 771376 \todo{add synergy ERC?}.
We thank Alexey Uvarovskii for code refactoring and helpful suggestions on the source code.
\bigskip

>>>>

\new{
These extensive benchmarks confirmed that our proposed combination of methods, i.e.\ using the shrunken means of residuals of VMRs for dimensionality reduction, is able to distinguish diverse cellular properties such as cell type, colorectal cancer stage (normal tissue, primary tumour, metastasis), embryonic stage, and germ layer (Fig.~\ref{fig:resource_usage}).
}

@@

SA and LPMK acknowledge funding by the Klaus Tschira Foundation (project 00.022.2019).
LPMK, MMB, LK, SC, and AMV acknowledge funding from the European Commission via ERC grant 771376.
We thank Alexey Uvarovskii for code refactoring and helpful suggestions on the source code.
\bigskip
